Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-12 snippets/iteration_diffusion.Rmd
Iterated Diffusion

@@

Diffusion is defined in terms of

@@

alpha= 0.1
rounds = 1000
ns = 6
nm = 3
states = seq(from=0,to=1,length.out = ns)
C = get.confusion.matrix(states,alpha)
```

Initialization
--------------

Create an arbitrary sender and receiver strategy.

@@

show(rec)

for (i in 1:rounds){
#   sen = get.nbr(sen,C)
  rec = get.nbr(rec,C)
}

show(rec)

>>>>

alpha= 0.2
rounds = 1000
ns = 7
nm = 4
states = seq(from=0,to=1,length.out = ns)
C = get.confusion.matrix(states,alpha)
```

@@

Diffusion is defined as simple matrix product for sender and receiver strategies.

@@

Iterated Diffusion
------------------

Create an arbitrary sender and receiver strategy, and iterate the diffusion process.

@@

for (i in 1:rounds){
  sen = get.nbr(sen,C)
  rec = get.nbr(rec,C)
}

show(rec)
show(sen)
